Data Migration under a Changing Schema in Ampersand

### 2023-12-10 2022Migration/articleMigrationFoIKS.tex
WIP

   The next section analyzes SCDMs with an eye on zero downtime and data quality.
   It sketches the outline of a procedure for SCDMs.
   Section~\ref{sct:Definitions} formalizes the concepts that we need to define the procedure.
   Section~\ref{sct:Generating} defines the algoritm for generating a migration system, to automate SCDMs.
   Section~\ref{sct:PoC} demonstrates the prototype of a migration system, which we used to validate our \ourtheory{} experimentally.
   For this purpose we have used the language Ampersand
   because its syntax and semantics correspond directly to the definitions in section~\ref{sct:Definitions}.

@@

   Exhibit D: When the last atom of {\tt A} is paired with an atom from {\tt B}, requirement~\ref{eqn:readyForMoC} is satisfied and the prototype informs the user to remove the migration system.

\subsection{Validation}
   The proof of concept gives but one example of something that works.
   In fact, having built prototypes increases our confidence, but cannot serve as a proof.
   This section argues the validity of our method.
   We take advantage of the formal definition of the generated migration system (section~\ref{sct:Generating}) to precisely state the assumptions and requirements of its validity.

@@

\section{Conclusions}
\label{sct:Conclusions}
   In this paper, we describe the data migration as going from an existing system to a desired one, where the schema changes.
   As Ampersand generates information systems, creating a new system can be a small task, allowing for incremental deployment of new features.
   We describe the parts of a system that have an effect on data pollution.
   We assume that the existing system does not violate any constraints of its schema, but address other forms of data pollution:
   constraints that are not in the schema but are in the desired schema are initially relaxed such that the business can start using the migration system, after which this form of data pollution needs to be addressed by human intervention.
   We propose a method for doing migration such that only a finite amount of human intervention is needed.
   Our method allows a system similar to the desired system to be used while the intervention takes place.

   Our proposed migration is certainly not the only approach one could think of.
   However, we have not come across other approaches that allow changing the schema in the presence of constraints.
   As such, we cannot compare our approach against other approaches.
   We envision that one day there will be multiple approaches for migration under a changing schema to choose from.
   For now, our next step is to implement the approach shown here into Ampersand.

>>>>

   The next section analyzes SCDMs with an eye on zero downtime and data quality.
   It sketches the outline of a procedure for SCDMs.
   Section~\ref{sct:Definitions} formalizes the concepts that we need to define the procedure.
   Section~\ref{sct:Generating} defines the algoritm for generating a migration system, to automate SCDMs.
   Section~\ref{sct:PoC} demonstrates the prototype of a migration system, which we used to verify our \ourtheory{} experimentally.
   We have used the language Ampersand for this purpose,
   because its syntax and semantics correspond directly to the definitions in section~\ref{sct:Definitions}.
   Finally, section~\ref{sct:Validation} discusses the validation of our \ourtheory{} by showing that all requirements are met.

@@

   Exhibit D: After the last atom of {\tt A} is paired with an atom from {\tt B}, requirement~\ref{eqn:readyForMoC} is satisfied and the prototype informs the user to remove the migration system.

\section{Validation}
\label{sct:Validation}
   The proof of concept gives but one example of something that works.
   In fact, having built prototypes increases our confidence, but cannot serve as a proof.
   This section argues the validity of our method.
   We take advantage of the formal definition of the generated migration system (section~\ref{sct:Generating}) to precisely state the assumptions and requirements of its validity.

@@

\section{Conclusion}
\label{sct:Conclusions}
   In this paper, we describe the data migration as going from an existing system to a desired one, where the schema changes.
   As Ampersand generates information systems, creating a new system can be a small task, allowing for incremental deployment of new features.
   We describe the parts of a system that have an effect on data pollution.
   We assume that the existing system does not violate any constraints of its schema, but address other forms of data pollution:
   constraints that are not in the schema but are in the desired schema are initially relaxed such that the business can start using the migration system, after which this form of data pollution needs to be addressed by human intervention.
   We propose a method for doing migration such that only a finite amount of human intervention is needed.
   Our method allows a system similar to the desired system to be used while the intervention takes place.

   The data migration we propose is certainly not the only approach one could think of.
   However, we have not come across other approaches that allow changing the schema in the presence of constraints.
   As such, we cannot compare our approach against other approaches.
   We envision that one day there will be multiple approaches for migration under a changing schema to choose from.
   For now, our next step is to implement the approach shown here into Ampersand.
